---
title: " "
output: 
  html_document
---
```{r include=F}

if (!require(RColorBrewer)){
  install.packages('RColorBrewer')
  require(RColorBrewer)
}

if (!require(wesanderson)){
  install.packages('wesanderson')
  require(wesanderson)
}

if (!require(tidyverse)){
  install.packages('tidyverse')
  require(tidyverse)
}

if (!require(lubridate)){
  install.packages('lubridate')
  require(lubridate)
}

library(knitr)
library(kableExtra)
library(gridExtra)
```

<br><br><br><br><br><br/>


[Back to models/plots](https://fieldofhats.github.io/MesoResultsHomePage/ )

# SC model

<br>

## year tabs above, SC model selection details 
#### significant covariates
#### waic for significant models
#### density and covariate estimates

<br>

### links to model selection by year:
all models waic ranking,

reversible jump MCMC,

parameter MCMC samples table and graphs.

[2016 model selection](https://fieldofhats.github.io/SC_model_2016/ )

[2017 model selection](https://fieldofhats.github.io/SC_model_2017/ )

[2018 model selection](https://fieldofhats.github.io/SC_model_2018/)

[2019 model selection](https://fieldofhats.github.io/SC_model_2019/ )


```{r, include = F}
## load top models
files<-list.files('./_data', pattern = '_density', full.names = T)
density.dat.covs <- tibble(filename = files, data.year = substring(files,9,12)) %>% # create a data frame
                                         # holding the file names
  mutate(file_contents = map(filename,          # read files into
           ~ readRDS(.)) # a new data column
        ) %>% 
  mutate(file_contents = map(file_contents, function(x) mutate(x,mode = as.character(mode)))) %>% 
  unnest(cols = c('file_contents')) %>% 
  select (-filename) %>% 
  filter(covs == 'D') %>% 
  arrange(species, data.year) %>% 
  mutate(mode = as.numeric(ifelse(mode == 'err', hdi_89pct_lower, mode)),
         sp_yr = as.factor(paste(species, data.year, sep = '_')))


## load all models:
## 2016 
# in.files<-list.files('./_data/2016', full.names = T)

yrs<-c('2016', '2017','2018', '2019')

.sum.dat<-tibble(data.year = rep(NA,4), data.tab = NA)  

i=1
for (i in 1:length(yrs)){
  in.files<-list.files(file.path('./_data',yrs[i]), full.names = T)
  
  sum.dat.temp <- tibble(filename = in.files) %>% # create a data frame
  mutate(file_contents = map(filename,          # read files into
           function(x) readRDS(x)$parameter.summary)) %>% # a new data column
  mutate(file_contents = map(file_contents, function(x) mutate(x,bayes_f_N03 = as.character(bayes_f_N03)))) %>%
  mutate(file_contents = map(file_contents, function(x) mutate(x,mode = as.character(mode)))) %>%
  mutate(file_contents = map(file_contents, function(x) mutate(x,bayes_P = as.character(bayes_P)))) %>%
  unnest(cols = c('file_contents')) %>% 
  #select(-filename) %>% 
  nest(data = everything())
  
  .sum.dat$data.year[i] <- yrs[i]
  .sum.dat$data.tab[i] <- sum.dat.temp
}

sum.dat<-.sum.dat %>% 
  unnest(data.tab) %>% 
  unnest(data.tab) %>%
  filter(param == 'D' & model == 'sc.fm1') %>% 
  mutate(species = sapply(strsplit(filename, "_"), function(x) x[3])) %>% 
  select(-filename) %>% 
  arrange(species, data.year)

sum.dat<-sum.dat %>% 
  mutate(mode = ifelse(mode == 'err', hdi_89pct_lower, mode),
         sp_yr = as.factor(paste(species, data.year, sep = '_'))) %>% 
  mutate(mode = as.numeric(mode)) 



  
  


```

<br><br><br><br><br><br>

## Density Estimates by Species, Year {.tabset}

### top model plots:

```{r echo = F, warning = F}
x.lab.in<-"Density per 100sqkm"
y.lab.in<-"species_year"

ggplot(data = density.dat.covs, aes(y = sp_yr, x = mode) ) +
  geom_errorbarh(aes(xmin = hdi_89pct_lower, xmax = hdi_89pct_upper)) +
  geom_point(shape = 21, color = 'blue', fill = 'white' , size = 3)   +
  xlab(x.lab.in) +
  ylab(y.lab.in)
```


### top model plots zoom:

```{r echo = F, warning = F}

y.in<-"sp_yr"
# y.in <-"species"

x.lab.in<-"Density per 100sqkm"
#y.lab.in<-"species_year"

x.max<-50
y.in<-sym(y.in)
ggplot(data = density.dat.covs, aes(y = !!y.in, x = mode) ) +
  geom_point(aes(x = hdi_89pct_lower, y = !!y.in), shape = '|', color = 'black', size = 3, position = position_nudge(y = .07)) +
  geom_point(aes(x = ifelse(hdi_89pct_upper > x.max,50, hdi_89pct_upper), y = !!y.in), shape = ifelse(density.dat.covs$hdi_89pct_upper > x.max, '>','|'), color = 'black', size = 3, position = position_nudge(y = .07)) +
  geom_segment(aes(x = hdi_89pct_lower, y = !!y.in, xend =ifelse(hdi_89pct_upper > x.max, 50,hdi_89pct_upper), yend = !!y.in)) +
  geom_point(shape = 21, color = 'blue', fill = 'white' , size = 3) +
  xlim(0,x.max) +
  xlab(x.lab.in) +
  ylab(y.lab.in)
```


### dot model plots:

```{r echo = F, warning = F}
x.lab.in<-"Density per 100sqkm"
y.lab.in<-"species_year"

ggplot(data = sum.dat, aes(y = sp_yr, x = mode) ) +
  geom_errorbarh(aes(xmin = hdi_89pct_lower, xmax = hdi_89pct_upper)) +
  geom_point(shape = 21, color = 'blue', fill = 'white' , size = 3)   +
  xlab(x.lab.in) +
  ylab(y.lab.in)
```


### dot model plots zoom:

```{r echo = F, warning = F}

y.in<-"sp_yr"
#y.in <-"species"

x.lab.in<-"Density per 100sqkm"
y.lab.in<-"species_year"

x.max<-50
y.in<-sym(y.in)
ggplot(data = sum.dat, aes(y = !!y.in, x = mode) ) +
  geom_point(aes(x = hdi_89pct_lower, y = !!y.in), shape = '|', color = 'black', size = 3, position = position_nudge(y = .07)) +
  geom_point(aes(x = ifelse(hdi_89pct_upper > x.max,50, hdi_89pct_upper), y = !!y.in), shape = ifelse(sum.dat$hdi_89pct_upper > x.max, '>','|'), color = 'black', size = 3, position = position_nudge(y = .07)) +
  geom_segment(aes(x = hdi_89pct_lower, y = !!y.in, xend =ifelse(hdi_89pct_upper > x.max, 50,hdi_89pct_upper), yend = !!y.in)) +
  geom_point(shape = 21, color = 'blue', fill = 'white' , size = 3) +
  xlim(0,x.max) +
  xlab(x.lab.in) +
  ylab(y.lab.in)
```

## 

<br>


####plot notes

top model plots:  
density estimate is from the top model by waic  
poorly converging models have been censored

dot model plots:  
estimates are from the dot (no covariate) model by species  
include poorly converging models, poor models often have very wide confidence intervals  
black bear did not converge very well, despite tight ci


<br><br><br><br><br>


```{r echo = F, warning=F}
### density estimates
density.dat<-readRDS('./_data/2019_density_sigCov_species.RDS')
cov.dat<-readRDS('./_data/2019_cov_significanceBySp.RDS')
```

<br><br><br><br>

##  density estimates and significant covs {.tabset}

### `r yr = '2016'; yr`

```{r echo = F, warning=F}
### density estimates
density.dat<-readRDS('./_data/2016_density_sigCov_species.RDS')
cov.dat<-readRDS('./_data/2016_cov_significanceBySp.RDS')
```

<br><br>

species density estimates (per 100 sqkm)

****************************************************************************************************************
```{r echo = F, warning=F}
density.dat %>% 
  filter(covs == 'D') %>% 
  mutate(density = mode) %>% 
  select(species, n_effective, density, hdi_89pct_lower, hdi_89pct_upper) %>% 
  kable(align = 'l', escape = F) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

<br><br>


<br><br>

Covariates on detection (x = not significant)

***********************************************************************************************************************

```{r, echo = F, warning=F}

cov.dat %>% 
  #column_to_rownames(var = 'covs') %>% 
  pivot_longer(-covs, names_to = 'species' , values_to = 'significance') %>% 
  mutate(cov.vals = ifelse(significance == 0, 'x', NA)) %>% 
  left_join(density.dat, by = c('species', 'covs')) %>% 
  mutate(cov.vals = ifelse(significance == 1, mode, cov.vals)) %>% 
  select(covs, species, cov.vals) %>%
  mutate(cov.vals = ifelse(is.na(cov.vals), 'x', cov.vals)) %>% 
  pivot_wider( values_from = cov.vals, names_from = species) %>%
  column_to_rownames(var = 'covs') %>% 
  kable(align = 'c', escape = F) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") 
  


```

### `r yr = '2017'; yr`


```{r echo = F, warning=F}
### density estimates
density.dat<-readRDS('./_data/2017_density_sigCov_species.RDS')
cov.dat<-readRDS('./_data/2017_cov_significanceBySp.RDS')
```

<br><br>

species density estimates (per 100 sqkm)

****************************************************************************************************************
```{r echo = F, warning=F}
density.dat %>% 
  filter(covs == 'D') %>% 
  mutate(density = mode) %>% 
  select(species, n_effective, density, hdi_89pct_lower, hdi_89pct_upper) %>% 
  kable(align = 'l', escape = F) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

<br><br>

####  bobcat and coyote did not converge well, estimates are suspect

<br><br>

Covariates on detection (x = not significant)

***********************************************************************************************************************

```{r, echo = F, warning=F}

cov.dat %>% 
  #column_to_rownames(var = 'covs') %>% 
  pivot_longer(-covs, names_to = 'species' , values_to = 'significance') %>% 
  mutate(cov.vals = ifelse(significance == 0, 'x', NA)) %>% 
  left_join(density.dat, by = c('species', 'covs')) %>% 
  mutate(cov.vals = ifelse(significance == 1, mode, cov.vals)) %>% 
  select(covs, species, cov.vals) %>%
  mutate(cov.vals = ifelse(is.na(cov.vals), 'x', cov.vals)) %>% 
  pivot_wider( values_from = cov.vals, names_from = species) %>%
  column_to_rownames(var = 'covs') %>% 
  kable(align = 'c', escape = F) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") 
  


```

### `r yr = '2018'; yr`


```{r echo = F, warning=F}
### density estimates
density.dat<-readRDS('./_data/2018_density_sigCov_species.RDS')
cov.dat<-readRDS('./_data/2018_cov_significanceBySp.RDS')
```

<br><br>

species density estimates (per 100 sqkm)

****************************************************************************************************************
```{r echo = F, warning=F}
density.dat %>% 
  filter(covs == 'D') %>% 
  mutate(density = mode) %>% 
  select(species, n_effective, density, hdi_89pct_lower, hdi_89pct_upper) %>% 
  mutate(density = ifelse(density == 'err', hdi_89pct_lower, density)) %>% 
  kable(align = 'l', escape = F) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

<br><br>

####  White tailed jackrabbit, poor model convergenc, estimate is suspect

<br><br>

Covariates on detection (x = not significant)

***********************************************************************************************************************

```{r, echo = F, warning=F}

cov.dat %>% 
  #column_to_rownames(var = 'covs') %>% 
  pivot_longer(-covs, names_to = 'species' , values_to = 'significance') %>% 
  mutate(cov.vals = ifelse(significance == 0, 'x', NA)) %>% 
  left_join(density.dat, by = c('species', 'covs')) %>% 
  mutate(cov.vals = ifelse(significance == 1, mode, cov.vals)) %>% 
  select(covs, species, cov.vals) %>%
  mutate(cov.vals = ifelse(is.na(cov.vals), 'x', cov.vals)) %>% 
  pivot_wider( values_from = cov.vals, names_from = species) %>%
  column_to_rownames(var = 'covs') %>% 
  kable(align = 'c', escape = F) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") 
  


```

### `r yr = '2019'; yr`

```{r echo = F, warning=F}
### density estimates
density.dat<-readRDS('./_data/2019_density_sigCov_species.RDS')
cov.dat<-readRDS('./_data/2019_cov_significanceBySp.RDS')
```

<br><br>

species density estimates (per 100 sqkm)

****************************************************************************************************************
```{r echo = F, warning=F}
density.dat %>% 
  filter(covs == 'D') %>% 
  mutate(density = mode) %>% 
  select(species, n_effective, density, hdi_89pct_lower, hdi_89pct_upper) %>% 
  kable(align = 'l', escape = F) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

<br><br><br><br>

Covariates on detection (x = not significant)

***********************************************************************************************************************

```{r, echo = F, warning=F}

cov.dat %>% 
  #column_to_rownames(var = 'covs') %>% 
  pivot_longer(-covs, names_to = 'species' , values_to = 'significance') %>% 
  mutate(cov.vals = ifelse(significance == 0, 'x', NA)) %>% 
  left_join(density.dat, by = c('species', 'covs')) %>% 
  mutate(cov.vals = ifelse(significance == 1, mode, cov.vals)) %>% 
  select(covs, species, cov.vals) %>%
  mutate(cov.vals = ifelse(is.na(cov.vals), 'x', cov.vals)) %>% 
  pivot_wider( values_from = cov.vals, names_from = species) %>%
  column_to_rownames(var = 'covs') %>% 
  kable(align = 'c', escape = F) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") 
  


```


##

## survey summary info:
<br><br/>
carnivore detections by survey season:
```{r echo=F, warnings = F}
#################### detections by sp table:
detections<-read.table('./_data/carnivorDetections2016to2019.txt', stringsAsFactors = F)
detection.mat<-as.matrix(detections[,-1], nrow = 4)
row.names(detection.mat)<-detections$data.year
detection.mat<-t(detection.mat)

kable(detection.mat) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```


<br><br/>

```{r, include = F}
########################
### plot operational days
###################
#### Custom wes_palette function
###  pal = a custom vector of colors, eg a wes pallet in a new order
## continuous will interpolate n2 colors in a new palette
## discrete will output collors n1 - n2 in the vector 
stretch.pal<-function (pal, name, n1 = 1,n2, type = c("discrete", "continuous")) 
{
  type <- match.arg(type)
  pal <- pal
  if (is.null(pal)) 
    stop("Palette not found.")
  if (missing(n2)) {
    n2 <- length(pal)
  }
  if (type == "discrete" && n2 > length(pal)) {
    stop("Number of requested colors greater than what palette can offer")
  }
  out <- switch(type, continuous = (grDevices::colorRampPalette(pal))(n2), 
                discrete = pal[n1:n2])
  structure(out, class = "palette", name = name)
}

### Plot operational dates:
pal <- wes_palette(10, name = "Darjeeling1", type = "continuous")

# image(volcano, col = pal)
# pal1<- wes_palette(10, name = "IsleofDogs1", type = "continuous")
# image(volcano, col = pal1)
# pal2<- wes_palette(10, name = "IsleofDogs2", type = "continuous")
# image(volcano, col = pal2)


## stretch.pal in functions


# pal <- wes_palette(name = "Darjeeling1")[c(1,4,3,2,5)]
pal <- stretch.pal(n2=10, pal=pal, type = "continuous", name = 'dar.new')
# pal <- stretch.pal(n1=3, n2=10, pal=pal, type = "discrete", name = 'dar.new')
# pal <- pal[1:8]
# image(volcano, col = pal)


all.blank<-read.table('./_data/2016to2019LongformCarnivors_20200422.txt', stringsAsFactors = F)

plot.blank<-all.blank 
## strings not factors or problems
plot.blank<-plot.blank %>%
  mutate(cells = substring(cell_site, 1,5)) %>%
  mutate(onDts = ifelse(is.na(count),NA, dtDate), offDts = ifelse(is.na(count) & !is.na(installed), dtDate, NA)) %>% 
  mutate(onDts = ymd(onDts), offDts = ymd(offDts))
# plot.blank<-plot.blank %>%
#   mutate(plot.sp = ifelse(is.na(!!sym(sp) == 0 ) | !!sym(sp) == 0, NA, dtDate)) %>%
#   mutate(plot.sp =ymd(plot.sp))

plot.blank<-plot.blank %>% 
  mutate(lure.day = ifelse(lureDays != 0 | is.na(lureDays), NA, dtDate)) %>% 
  mutate(lure.day = ymd(lure.day))
## View (plot.blank)


```




```{r, include = F, as.is = T, message = F}
years=unique(plot.blank$data.year)
#bl.plot <- plot.blank
plot.list<-list()
for(i in 1 : length(years) ){
  bl.plot<-plot.blank %>% filter(data.year == years[i])
  installed.days<-sum(bl.plot$installed, na.rm = T)
  op.days<-sum(!is.na(bl.plot$count))
  bl<-ggplot(data = bl.plot, aes(y=factor(year_cell_site)))
  plot.list[[years[i]]]<- bl + geom_path(aes(x=offDts), size = 1) +
    geom_path(aes(x=onDts), color = pal[2], size = 2) +
    geom_point(aes(x=lure.day), shape = 21, fill = pal[3], size = 2) +
    xlab('date') + ylab('year_cell_site') + 
    ggtitle(paste0('days intalled:  ',installed.days, '     operational days:  ', op.days, '   op/installed:  ', round(op.days/installed.days, 2)))
}

```



#### camera operational days by year


##  {.tabset}

### `r in.yr<-years[[1]]; in.yr`

```{r, echo=F, message=F, warning=F}
plot.list[[in.yr]]
```

### `r in.yr<-years[[2]]; in.yr`

```{r, echo=F, message=F, warning=F}
plot.list[[in.yr]]
```

### `r in.yr<-years[[3]]; in.yr`

```{r, echo=F, message=F, warning=F}
plot.list[[in.yr]]
```

### `r in.yr<-years[[4]]; in.yr`

```{r, echo=F, message=F, warning=F}
plot.list[[in.yr]]
```

# {-}





