---
title: " "
output: 
  html_document
---
```{r include=F}

if (!require(RColorBrewer)){
  install.packages('RColorBrewer')
  require(RColorBrewer)
}

if (!require(wesanderson)){
  install.packages('wesanderson')
  require(wesanderson)
}

if (!require(tidyverse)){
  install.packages('tidyverse')
  require(tidyverse)
}

if (!require(lubridate)){
  install.packages('lubridate')
  require(lubridate)
}

library(knitr)
library(kableExtra)
library(gridExtra)
```

<br><br><br><br><br><br/>


[Back to models/plots](https://fieldofhats.github.io/MesoResultsHomePage/ )

# SC model

<br>

## year tabs above, SC model selection details 
#### significant covariates
#### waic for significant models
#### density and covariate estimates

<br>

### links to model selection by year:
all models waic ranking,

reversible jump MCMC,

parameter MCMC samples table and graphs.

[2016 model selection - stand by](https://fieldofhats.github.io/SC_model_2016/ )

[2017 model selection](https://fieldofhats.github.io/SC_model_2017/ )

[2018 model selection](https://fieldofhats.github.io/SC_model_2018/)

[2019 model selection](https://fieldofhats.github.io/SC_model_2019/ )


```{r echo = F, warning=F}
### density estimates
density.dat<-readRDS('./_data/2019_density_sigCov_species.RDS')
cov.dat<-readRDS('./_data/2019_cov_significanceBySp.RDS')
```

<br><br><br><br>

##  density estimates and significant covs {.tabset}

### `r yr = '2016'; yr`

stand by

### `r yr = '2017'; yr`


```{r echo = F, warning=F}
### density estimates
density.dat<-readRDS('./_data/2017_density_sigCov_species.RDS')
cov.dat<-readRDS('./_data/2017_cov_significanceBySp.RDS')
```

<br><br>

species density estimates (per 100 sqkm)

****************************************************************************************************************
```{r echo = F, warning=F}
density.dat %>% 
  filter(covs == 'D') %>% 
  mutate(density = mode) %>% 
  select(species, n_effective, density, hdi_89pct_lower, hdi_89pct_upper) %>% 
  kable(align = 'l', escape = F) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

<br><br>

####  bobcat and coyote did not converge well, estimates are suspect

<br><br>

Covariates on detection (x = not significant)

***********************************************************************************************************************

```{r, echo = F, warning=F}

cov.dat %>% 
  #column_to_rownames(var = 'covs') %>% 
  pivot_longer(-covs, names_to = 'species' , values_to = 'significance') %>% 
  mutate(cov.vals = ifelse(significance == 0, 'x', NA)) %>% 
  left_join(density.dat, by = c('species', 'covs')) %>% 
  mutate(cov.vals = ifelse(significance == 1, mode, cov.vals)) %>% 
  select(covs, species, cov.vals) %>%
  mutate(cov.vals = ifelse(is.na(cov.vals), 'x', cov.vals)) %>% 
  pivot_wider( values_from = cov.vals, names_from = species) %>%
  column_to_rownames(var = 'covs') %>% 
  kable(align = 'c', escape = F) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") 
  


```

### `r yr = '2018'; yr`


```{r echo = F, warning=F}
### density estimates
density.dat<-readRDS('./_data/2018_density_sigCov_species.RDS')
cov.dat<-readRDS('./_data/2018_cov_significanceBySp.RDS')
```

<br><br>

species density estimates (per 100 sqkm)

****************************************************************************************************************
```{r echo = F, warning=F}
density.dat %>% 
  filter(covs == 'D') %>% 
  mutate(density = mode) %>% 
  select(species, n_effective, density, hdi_89pct_lower, hdi_89pct_upper) %>% 
  mutate(density = ifelse(density == 'err', hdi_89pct_lower, density)) %>% 
  kable(align = 'l', escape = F) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

<br><br>

####  White tailed jackrabbit, poor model convergenc, estimate is suspect

<br><br>

Covariates on detection (x = not significant)

***********************************************************************************************************************

```{r, echo = F, warning=F}

cov.dat %>% 
  #column_to_rownames(var = 'covs') %>% 
  pivot_longer(-covs, names_to = 'species' , values_to = 'significance') %>% 
  mutate(cov.vals = ifelse(significance == 0, 'x', NA)) %>% 
  left_join(density.dat, by = c('species', 'covs')) %>% 
  mutate(cov.vals = ifelse(significance == 1, mode, cov.vals)) %>% 
  select(covs, species, cov.vals) %>%
  mutate(cov.vals = ifelse(is.na(cov.vals), 'x', cov.vals)) %>% 
  pivot_wider( values_from = cov.vals, names_from = species) %>%
  column_to_rownames(var = 'covs') %>% 
  kable(align = 'c', escape = F) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") 
  


```

### `r yr = '2019'; yr`

```{r echo = F, warning=F}
### density estimates
density.dat<-readRDS('./_data/2019_density_sigCov_species.RDS')
cov.dat<-readRDS('./_data/2019_cov_significanceBySp.RDS')
```

<br><br>

species density estimates (per 100 sqkm)

****************************************************************************************************************
```{r echo = F, warning=F}
density.dat %>% 
  filter(covs == 'D') %>% 
  mutate(density = mode) %>% 
  select(species, n_effective, density, hdi_89pct_lower, hdi_89pct_upper) %>% 
  kable(align = 'l', escape = F) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

<br><br><br><br>

Covariates on detection (x = not significant)

***********************************************************************************************************************

```{r, echo = F, warning=F}

cov.dat %>% 
  #column_to_rownames(var = 'covs') %>% 
  pivot_longer(-covs, names_to = 'species' , values_to = 'significance') %>% 
  mutate(cov.vals = ifelse(significance == 0, 'x', NA)) %>% 
  left_join(density.dat, by = c('species', 'covs')) %>% 
  mutate(cov.vals = ifelse(significance == 1, mode, cov.vals)) %>% 
  select(covs, species, cov.vals) %>%
  mutate(cov.vals = ifelse(is.na(cov.vals), 'x', cov.vals)) %>% 
  pivot_wider( values_from = cov.vals, names_from = species) %>%
  column_to_rownames(var = 'covs') %>% 
  kable(align = 'c', escape = F) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") 
  


```


##

## survey summary info:
<br><br/>
carnivore detections by survey season:
```{r echo=F, warnings = F}
#################### detections by sp table:
detections<-read.table('./_data/carnivorDetections2016to2019.txt', stringsAsFactors = F)
detection.mat<-as.matrix(detections[,-1], nrow = 4)
row.names(detection.mat)<-detections$data.year
detection.mat<-t(detection.mat)

kable(detection.mat) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```


<br><br/>

```{r, include = F}
########################
### plot operational days
###################
#### Custom wes_palette function
###  pal = a custom vector of colors, eg a wes pallet in a new order
## continuous will interpolate n2 colors in a new palette
## discrete will output collors n1 - n2 in the vector 
stretch.pal<-function (pal, name, n1 = 1,n2, type = c("discrete", "continuous")) 
{
  type <- match.arg(type)
  pal <- pal
  if (is.null(pal)) 
    stop("Palette not found.")
  if (missing(n2)) {
    n2 <- length(pal)
  }
  if (type == "discrete" && n2 > length(pal)) {
    stop("Number of requested colors greater than what palette can offer")
  }
  out <- switch(type, continuous = (grDevices::colorRampPalette(pal))(n2), 
                discrete = pal[n1:n2])
  structure(out, class = "palette", name = name)
}

### Plot operational dates:
pal <- wes_palette(10, name = "Darjeeling1", type = "continuous")

# image(volcano, col = pal)
# pal1<- wes_palette(10, name = "IsleofDogs1", type = "continuous")
# image(volcano, col = pal1)
# pal2<- wes_palette(10, name = "IsleofDogs2", type = "continuous")
# image(volcano, col = pal2)


## stretch.pal in functions


# pal <- wes_palette(name = "Darjeeling1")[c(1,4,3,2,5)]
pal <- stretch.pal(n2=10, pal=pal, type = "continuous", name = 'dar.new')
# pal <- stretch.pal(n1=3, n2=10, pal=pal, type = "discrete", name = 'dar.new')
# pal <- pal[1:8]
# image(volcano, col = pal)


all.blank<-read.table('./_data/2016to2019LongformCarnivors_20200422.txt', stringsAsFactors = F)

plot.blank<-all.blank 
## strings not factors or problems
plot.blank<-plot.blank %>%
  mutate(cells = substring(cell_site, 1,5)) %>%
  mutate(onDts = ifelse(is.na(count),NA, dtDate), offDts = ifelse(is.na(count) & !is.na(installed), dtDate, NA)) %>% 
  mutate(onDts = ymd(onDts), offDts = ymd(offDts))
# plot.blank<-plot.blank %>%
#   mutate(plot.sp = ifelse(is.na(!!sym(sp) == 0 ) | !!sym(sp) == 0, NA, dtDate)) %>%
#   mutate(plot.sp =ymd(plot.sp))

plot.blank<-plot.blank %>% 
  mutate(lure.day = ifelse(lureDays != 0 | is.na(lureDays), NA, dtDate)) %>% 
  mutate(lure.day = ymd(lure.day))
## View (plot.blank)


```




```{r, include = F, as.is = T, message = F}
years=unique(plot.blank$data.year)
#bl.plot <- plot.blank
plot.list<-list()
for(i in 1 : length(years) ){
  bl.plot<-plot.blank %>% filter(data.year == years[i])
  installed.days<-sum(bl.plot$installed, na.rm = T)
  op.days<-sum(!is.na(bl.plot$count))
  bl<-ggplot(data = bl.plot, aes(y=factor(year_cell_site)))
  plot.list[[years[i]]]<- bl + geom_path(aes(x=offDts), size = 1) +
    geom_path(aes(x=onDts), color = pal[2], size = 2) +
    geom_point(aes(x=lure.day), shape = 21, fill = pal[3], size = 2) +
    xlab('date') + ylab('year_cell_site') + 
    ggtitle(paste0('days intalled:  ',installed.days, '     operational days:  ', op.days, '   op/installed:  ', round(op.days/installed.days, 2)))
}

```



#### camera operational days by year


##  {.tabset}

### `r in.yr<-years[[1]]; in.yr`

```{r, echo=F, message=F, warning=F}
plot.list[[in.yr]]
```

### `r in.yr<-years[[2]]; in.yr`

```{r, echo=F, message=F, warning=F}
plot.list[[in.yr]]
```

### `r in.yr<-years[[3]]; in.yr`

```{r, echo=F, message=F, warning=F}
plot.list[[in.yr]]
```

### `r in.yr<-years[[4]]; in.yr`

```{r, echo=F, message=F, warning=F}
plot.list[[in.yr]]
```

# {-}





